The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-05 writing/draft3/draft6.tex
writing
working hardly

	Both precipitation and temperature datasets are daily while the yield data are yearly by its nature. Hence, in order to proceed with the analysis, the daily precipitation and temperature data had to be converted
into a county-level yearly panel. The first step of this procedure was averaging the gridded weather data over the counties of Kenya resulting in a single daily time series for each county. In the next step, we aggregated the resulting county level time series temporally to obtain yearly time series using the seasonal crop calendar which is available at the website of FEWS~NET. We separated the counties of Kenya into two groups, such that the crop calendar can be considered homogeneous within each group. The groups are: \textit{(i)} Arid and semi-arid (ASAL) counties and \textit{(ii)} non-ASAL as defined by the ASAL Stakeholders Forum (ASF). In particular, the ASAL counties include ..see appendix..\footnote{The crop calendar is probably not exactly the same for all counties within each group, however, it is similar enough so that it can be considered homogeneous within the groups. To a certain extent, the crop calendar is likely to differ even within a single county. However, considering the information provided by ASF and FEWS NET and our intermediate results, we opted for the two groups as a compromise between accuracy and complexity.}

 In particular, we   We only considered weather data during the rainy seasons which we defined as follows, using the classification of...

>>>>

	Both precipitation and temperature datasets are daily while the yield data are yearly by its nature. Hence, in order to proceed with the analysis, the daily precipitation and temperature data had to be converted
into a county-level yearly panel. The first step of this procedure was averaging the gridded weather data over the counties of Kenya resulting in a single daily time series for each county. In the next step, we aggregated the resulting county level time series temporally to obtain yearly time series using the seasonal crop calendar which is available at the website of FEWS~NET. We separated the counties of Kenya into two groups, such that the crop calendar can be considered homogeneous within each group. The groups are: \textit{(i)} Arid and semi-arid (ASAL) counties and \textit{(ii)} non-ASAL counties as defined by the ASAL Stakeholders Forum (ASF). For the list of counties in each of the groups see table~\ref{ASAL} in the appendix. \footnote{The crop calendar is probably not exactly the same for all counties within each group, however, it is similar enough so that it can be considered homogeneous within the groups. To a certain extent, the crop calendar is likely to differ even within a single county. However, considering the information provided by ASF, FEWS NET and accounting for our intermediate results, we opted for the two groups as a compromise between accuracy and complexity.}.

In terms of weather, the most relevant periods for yield are the rainy seasons.
Therefore, we only considered weather during the rainy seasons for our analysis. According to FEWS~NET, the ASAL counties have two distinct rainy seasons while the non-ASAL counties have one longer rainy seasons. The two rainy seasons of the ASAL counties are: \textit{(i)} March-May and \textit{(ii)} October-December. In the non-ASAL area, the rainy season is in March-August.

Hence, for the ASAL counties, we aggregated daily precipitation and temperature over October, November and December of the previous year and May, April, May of the current year  to get single value of the weather variables for each county and year. For the non-ASAL counties we aggregated the daily weather values over March, April, May, June, July and August to obtain yearly values.
